{$\ch_2(\tf)$ Optimality Conditions for a Finite-time Horizon\thanksref{mytitlenote}}

### 2019-05-01 FH Optimality Conditions Paper.tex
fixed bibliography

\end{frontmatter}
%Introduction
%Introduction
\section{Introduction}
%Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as signal propagation in the nervous system\cite{kellems2009low}, heat dissipation, prediction of major weather events \cite{BoyP11,Sha03,Ant05}. 
Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as \textcolor{red}{signal propagation in the nervous system\cite{kellems2009low};  the synthesis  of
interconnect \cite{BonD07} and semiconductor devices \cite{Hess2014}; large-scale inverse problem,
 \cite{Druskin2011solution,Lieberman2010,de2015nonlinear}; and prediction of major weather events \cite{BoyP11,Sha03,Ant05}.}
The need for  detailed  models due to the increasing demand for greater resolution leads to  
large-scale dynamical systems, posing tremendous computational difficulties when applied in numerical simulations. In order to overcome these challenges, we perform  model reduction where we replace the large-scale dynamics with high-fidelity reduced representations.

>>>>

\end{frontmatter}
%Introduction
%Introduction
\section{Introduction}
%Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as signal propagation in the nervous system\cite{kellems2009low}, heat dissipation, prediction of major weather events \cite{BoyP11,Sha03,Ant05}. 
Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as \textcolor{red}{signal propagation in the nervous system\cite{kellems2009low};  the synthesis  of
interconnect \cite{BonD07} and semiconductor devices \cite{Hess2014}; large-scale inverse problem,
 \cite{Druskin2011solution,Lieberman2010,de2015nonlinear}; and prediction of major weather events \cite{Ant05}.}
The need for  detailed  models due to the increasing demand for greater resolution leads to  
large-scale dynamical systems, posing tremendous computational difficulties when applied in numerical simulations. In order to overcome these challenges, we perform  model reduction where we replace the large-scale dynamics with high-fidelity reduced representations.
